
---
output:
  pdf_document: default
  html_document: default
  word_document: default
---
---
title: "Gendergit"
output:
  pdf_document: default
  word_document: default

```{r setup, include=F, cache=F}

knitr::opts_chunk$set(comment=NA,
                      error=F,            # check output carefully for errors
                      warning=F,
                      message=F,
                      cache=T, autodep=T, # but set these to false if necessary
                      echo=F)  
 knitr::opts_chunk$set(dev="pdf")
# omit source code from output
# you can override these global settings on particular chunks
# more libraries here
library("litdata")
library("dplyr")
library ("tidyr")
library ("igraph")
```

```{r full network information}

#read in the data

authors <- read.table("/Users/Samuel/Downloads/R work /isfdb-tsv/tsv/authors.tsv", sep="\t", 
                      header=T, stringsAsFactors=F, quote="", 
                      comment.char="", encoding="UTF-8", fileEncoding="UTF-8")
 
pubs <- read.table("tsv/pubs.tsv", sep="\t", 
                   header=T, stringsAsFactors=F, quote="", 
                   comment.char="", encoding="UTF-8", fileEncoding="UTF-8")

titles <- read.table("tsv/titles.tsv", sep="\t", 
                     header=T, stringsAsFactors=F, quote="", 
                     comment.char="", encoding="UTF-8", fileEncoding="UTF-8")


pub_content <- read.table("tsv/pub_content.tsv", sep="\t", 
                          header=T, stringsAsFactors=F, quote="", 
                          comment.char="", encoding="UTF-8", 
                          fileEncoding="UTF-8")


canonical_authors <- read.table("tsv/canonical_author.tsv", sep="\t", 
                                header=T, stringsAsFactors=F, quote="", 
                                comment.char="", encoding="UTF-8", 
                                fileEncoding="UTF-8")

#filter out the magazines of interest 
#Astounding Stories & Wonder Stories appear twice because they went through name changes

our_canon <- pubs  %>% filter(str_detect(pub_title, ("^Amazing Stories|^Astounding Stories|^Wonder Stories|^Thrilling Wonder|^Planet Stories|^Startling Stories|^Fantastic Adventures|^Weird Tales|^Astounding Science-Fiction")))

#join publication information to information about the titles

our_canon_df <- pub_content  %>% inner_join (our_canon, by="pub_id")  %>%
inner_join (titles, by="title_id")

#join that dataframe to information about the authors

our_canon_df <- canonical_authors  %>%
inner_join (our_canon_df, by="title_id")  %>%
inner_join (authors, by="author_id")

#select four columns: publication title, publication year, title and author

our_canon_df <- our_canon_df %>% select (pub_title, pub_year, title_title, author_canonical)

#change names of publications to one word for easier searching/graphing
#and to compensate for database inconsistencies 
#for example: Astounding being named "Astounding Science Fiction" for one entry
#and "Astounding Science-Fiction" for the next

giant_network <- our_canon_df   %>%  
  mutate (pub_title= gsub ("Weird Tales.*", "Weird", pub_title))  %>% 
  mutate (pub_title =gsub ("Amazing Stories, .*", "Amazing", pub_title))  %>%  
  mutate (pub_title=gsub ("Amazing Stories.*, .*", "Amazing", pub_title)) %>% 
  mutate (pub_title=gsub (".*Wonder Stories, .*", "Wonder", pub_title))  %>% 
  mutate (pub_title=gsub ("Wonder Stories.*, .*", "Wonder", pub_title))  %>% 
  mutate (pub_title=gsub ("Astounding Stories .*, .*", "Astounding", pub_title))   %>% 
  mutate (pub_title=gsub ("Astounding Science-Fiction, .*", "Astounding", pub_title)) %>%
  mutate (pub_title=gsub ("Astounding Stories, .*", "Astounding", pub_title)) %>%
  mutate (pub_title=gsub ("Startling Stories, .*", "Startling", pub_title)) %>%
  mutate (author_canonical=gsub ("^John W. .*", "Campbell", author_canonical)) %>%
    mutate (pub_title=gsub ("^Planet Stories, .*", "Planet", pub_title)) %>%
   mutate (pub_title=gsub ("^Fantastic Adventures, .*", "Fantastic", pub_title)) 

```
  
 Full network, greater than 5
```{r, fig.height=8, fig.width=8, fig.cap= "All authors with more than 5 works (1926-1946)" }

#select the years of interest 
#filter to only include higher count authors (+5 publications)

giant_network_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946")))  %>%
  distinct ()  %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix
#prepare matrix for graphing

(set.seed(42)) 

 giant_network_matrix <- as.matrix (giant_network_df) 
 giant_network_graph <- graph.edgelist (giant_network_matrix, directed=F) 
  giant_network_graph <- simplify (giant_network_graph)

#simplify edges: one edge per author connection (rather than one edge per publication)
#so if Lovecraft ever published in Weird Tales he gets an edge
#it doesn't matter if he's published 5 or 50 times 

#add shapes to nodes  
V(giant_network_graph)$size <- 3
vshape <- rep("circle", vcount(giant_network_graph))
vshape [V(giant_network_graph)$name == "Astounding"] <- "rectangle"
vshape [V(giant_network_graph)$name=="Amazing"]<-"rectangle"
vshape [V(giant_network_graph)$name=="Weird"]<-"square"
vshape [V(giant_network_graph)$name=="Wonder"]<-"square"
vshape [V(giant_network_graph)$name=="Fantastic"]<-"rectangle"
vshape [V(giant_network_graph)$name=="Startling"]<-"square"
vshape [V(giant_network_graph)$name=="Planet"]<-"rectangle"
V(giant_network_graph)$shape <-vshape

#add colors to nodes

vcolors <- rep("orange", vcount(giant_network_graph))
vcolors [V(giant_network_graph)$name == "Astounding"] <- "yellow"
vcolors [V(giant_network_graph)$name == "Amazing"] <- "cyan"
vcolors [V(giant_network_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(giant_network_graph)$name == "Wonder"] <- "plum"
vcolors [V(giant_network_graph)$name == "Fantastic"] <- "gray"
vcolors [V(giant_network_graph)$name == "Startling"] <- "red"
vcolors [V(giant_network_graph)$name == "Planet"] <- "springgreen4"

plot (giant_network_graph, vertex.color=vcolors, vertex.size=4, vertex.label=NA) 


```
Full Network, Greater than 5, Black and White 

```{r, fig.height=8, fig.width=8, fig.cap= "All authors with more than 5 works (1926-1946)" }

#select the years of interest 
#filter to only include higher count authors (+5 publications)

giant_network_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946")))  %>%
  distinct ()  %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix
#prepare matrix for graphing

(set.seed(42)) 

 giant_network_matrix <- as.matrix (giant_network_df) 
 giant_network_graph <- graph.edgelist (giant_network_matrix, directed=F) 
  giant_network_graph <- simplify (giant_network_graph)

#simplify edges: one edge per author connection (rather than one edge per publication)
#so if Lovecraft ever published in Weird Tales he gets an edge
#it doesn't matter if he's published 5 or 50 times 


#add colors to nodes

#add shapes to nodes
V(giant_network_graph)$size <- 3
vshape <- rep("circle", vcount(giant_network_graph))
vshape [V(giant_network_graph)$name == "Astounding"] <- "rectangle"
vshape [V(giant_network_graph)$name=="Amazing"]<-"rectangle"
vshape [V(giant_network_graph)$name=="Weird"]<-"square"
vshape [V(giant_network_graph)$name=="Wonder"]<-"square"
vshape [V(giant_network_graph)$name=="Fantastic"]<-"sphere"
vshape [V(giant_network_graph)$name=="Starling"]<-"sphere"
vshape [V(giant_network_graph)$name=="Planet"]<-"rectangle"
V(giant_network_graph)$shape <-vshape

#add colors to nodes
vcolors <- rep("white", vcount(giant_network_graph))
vcolors [V(giant_network_graph)$name == "Astounding"] <- "black"
vcolors [V(giant_network_graph)$name == "Amazing"] <- "dimgrey"
vcolors [V(giant_network_graph)$name == "Weird"] <- "black"
vcolors [V(giant_network_graph)$name == "Wonder"] <- "dimgrey"
vcolors [V(giant_network_graph)$name == "Fantastic"] <- "black"
vcolors [V(giant_network_graph)$name == "Startling"] <- "dimgrey"
vcolors [V(giant_network_graph)$name == "Planet"] <- "white"


plot (giant_network_graph, vertex.color=vcolors, vertex.label=NA) 

```

Full Network, More than 10 authors 
```{r, fig.height=8, fig.width=8 }

#select the years of interest 
#filter to only include higher count authors (+10 publications)

giant_network_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946")))  %>%
  distinct ()  %>% group_by (author_canonical)  %>% filter (n() > 10) %>%
  select (pub_title, author_canonical)

#turn data into matrix
#prepare matrix for graphing

(set.seed(42)) 

 giant_network_matrix <- as.matrix (giant_network_df) 
 giant_network_graph <- graph.edgelist (giant_network_matrix, directed=F) 
  giant_network_graph <- simplify (giant_network_graph)

#simplify edges: one edge per author connection (rather than one edge per publication)
#so if Lovecraft ever published in Weird Tales he gets an edge
#it doesn't matter if he's published 5 or 50 times 

#add shapes to nodes
  
  V(giant_network_graph)$size <- 3
vshape <- rep("circle", vcount(giant_network_graph))
vshape [V(giant_network_graph)$name == "Astounding"] <- "rectangle"
vshape [V(giant_network_graph)$name=="Amazing"]<-"rectangle"
vshape [V(giant_network_graph)$name=="Weird"]<-"square"
vshape [V(giant_network_graph)$name=="Wonder"]<-"square"
vshape [V(giant_network_graph)$name=="Fantastic"]<-"rectangle"
vshape [V(giant_network_graph)$name=="Startling"]<-"square"
vshape [V(giant_network_graph)$name=="Planet"]<-"rectangle"
V(giant_network_graph)$shape <-vshape

#add colors to nodes

vcolors <- rep("orange", vcount(giant_network_graph))
vcolors [V(giant_network_graph)$name == "Astounding"] <- "yellow"
vcolors [V(giant_network_graph)$name == "Amazing"] <- "cyan"
vcolors [V(giant_network_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(giant_network_graph)$name == "Wonder"] <- "plum"
vcolors [V(giant_network_graph)$name == "Fantastic"] <- "gray"
vcolors [V(giant_network_graph)$name == "Startling"] <- "red"
vcolors [V(giant_network_graph)$name == "Planet"] <- "springgreen4"

plot (giant_network_graph, vertex.color=vcolors, vertex.size=4, vertex.label=NA) 

```
Full Network, More than 15 authors 

```{r, fig.height=8, fig.width=8 }

#select the years of interest 
#filter to only include higher count authors (+15 publications)

giant_network_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946")))  %>%
  distinct ()  %>% group_by (author_canonical)  %>% filter (n() > 15) %>%
  select (pub_title, author_canonical)

#turn data into matrix
#prepare matrix for graphing

(set.seed(42)) 

 giant_network_matrix <- as.matrix (giant_network_df) 
 giant_network_graph <- graph.edgelist (giant_network_matrix, directed=F) 
  giant_network_graph <- simplify (giant_network_graph)

#simplify edges: one edge per author connection (rather than one edge per publication)
#so if Lovecraft ever published in Weird Tales he gets an edge
#it doesn't matter if he's published 5 or 50 times 


#add colors to nodes

vcolors <- rep("orange", vcount(giant_network_graph))
vcolors [V(giant_network_graph)$name == "Astounding"] <- "yellow"
vcolors [V(giant_network_graph)$name == "Amazing"] <- "cyan"
vcolors [V(giant_network_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(giant_network_graph)$name == "Wonder"] <- "plum"
vcolors [V(giant_network_graph)$name == "Fantastic"] <- "gray"
vcolors [V(giant_network_graph)$name == "Startling"] <- "red"
vcolors [V(giant_network_graph)$name == "Planet"] <- "springgreen4"

plot (giant_network_graph, vertex.color=vcolors, vertex.size=4, vertex.label=NA) 


```
Women authors, All, 1926-1946 

``` {r fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

#add shapes to nodes

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

V(pulp_women_graph)$size <- 3
vshape <- rep("circle", vcount(pulp_women_graph))
vshape [V(pulp_women_graph)$name == "Astounding"] <- "rectangle"
vshape [V(pulp_women_graph)$name=="Amazing"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Weird"]<-"square"
vshape [V(pulp_women_graph)$name=="Wonder"]<-"square"
vshape [V(pulp_women_graph)$name=="Fantastic"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Startling"]<-"square"
vshape [V(pulp_women_graph)$name=="Planet"]<-"rectangle"
V(pulp_women_graph)$shape <-vshape


#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label=NA, vertex.size=5)


```
Women authors, 1926-1931

``` {r, fig.cap="Gender in SF Pulps, 1926-1931", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931"))) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))


pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)

```
Women authors, 1931-1938 

``` {r, fig.cap="Gender in SF Pulps, 1931-1938", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1932|^1933|^1934|^1935|^1936|^1937"))) %>%
  select (pub_title, author_canonical)


#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)


```` 
Women authors, 1939-1946 

``` {r, fig.cap="Gender in SF Pulps, 1931-1938", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral|^Z. B. Bishop|^.Cabral|^Loretta Burrough"))) %>%
  filter (str_detect (pub_year, ("^1939|^1940|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  select (pub_title, author_canonical)


#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)


```` 

Women authors who wrote more than 5 works, 1926-1946 
``` {r, fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add shapes to nodes
V(pulp_women_graph)$size <- 3
vshape <- rep("circle", vcount(pulp_women_graph))
vshape [V(pulp_women_graph)$name == "Astounding"] <- "rectangle"
vshape [V(pulp_women_graph)$name=="Amazing"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Weird"]<-"square"
vshape [V(pulp_women_graph)$name=="Wonder"]<-"square"
vshape [V(pulp_women_graph)$name=="Fantastic"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Fantastic"]<-"square"
vshape [V(pulp_women_graph)$name=="Planet"]<-"rectangle"
V(pulp_women_graph)$shape <-vshape
#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "yellow"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.color="black", vertex.label.family="Times",vertex.label.cex=.5, vertex.size=6)

```

Women authors who wrote more than 5 works, 1926-1931 

``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)

vcount (pulp_women_graph)
ecount(pulp_women_graph)
```
Women who wrote more than 5 works, 1932-1938, Unsimplified 
``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1932|^1933|^1934|^1935|^1936|^1937|^1938"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)

vcount (pulp_women_graph)
ecount(pulp_women_graph)
```
Women who wrote more than 5 works, 1932-1938, Simplified 

``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1932|^1933|^1934|^1935|^1936|^1937|^1938"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify(pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)

vcount (pulp_women_graph)
ecount(pulp_women_graph)
```

Women who wrote more than 5 works, 1938-1946, unsimplifed 
``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)

vcount (pulp_women_graph)
ecount(pulp_women_graph)
````
Women who wrote more than 5 works, 1938-1946, Simplified 

``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 5) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph) 
                      
#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.color="black", vertex.label.family="Times",vertex.label.cex=.75, vertex.size=6)


vcount (pulp_women_graph)
ecount(pulp_women_graph)
````

Women who wrote more than 10 works 
``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 10) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "yellow"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.color="black", vertex.label.family="Times",vertex.label.cex=.75, vertex.size=6)

vcount (pulp_women_graph)
ecount(pulp_women_graph)
```

Women who wrote more than 15 publications 
``` {r, fig.cap="Women with more than 15 publications", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 15) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)
pulp_women_graph <- simplify (pulp_women_graph)

#add shapes to nodes
V(pulp_women_graph)$size <- 3
vshape <- rep("circle", vcount(pulp_women_graph))
vshape [V(pulp_women_graph)$name == "Astounding"] <- "rectangle"
vshape [V(pulp_women_graph)$name=="Amazing"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Weird"]<-"square"
vshape [V(pulp_women_graph)$name=="Wonder"]<-"square"
vshape [V(pulp_women_graph)$name=="Fantastic"]<-"rectangle"
vshape [V(pulp_women_graph)$name=="Startling"]<-"square"
vshape [V(pulp_women_graph)$name=="Planet"]<-"rectangle"
V(pulp_women_graph)$shape <-vshape

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "yellow"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.color="black", vertex.label.family="Times",vertex.label.cex=.6, vertex.size=6)


```

Women with more than 20 publications 

``` {r, fig.cap="Gender in SF Pulps, 1926-1946", fig.width=8, fig.height=8}

#filter known female authors and years of interest

pulp_women_df <- giant_network  %>%  
  select (pub_year, pub_title, author_canonical) %>%
  filter (str_detect (author_canonical, ("^Leigh Brackett|^Frances M. Deegan|^Merab Eberle|^Sophie Wenzel Ellis|^Mona Farnsworth|^Mrs. Lee Hawkins Garby|^Frances Garfield|^L. Taylor Hansen|^Clare Winger Harris|^Hazel Heald|^E. Mayne Hull|^Amelia Reynolds Long|^Lilith Lorraine|^Kathleen Ludwick|^C. L. Moore|^Dorothy Quick|^Kaye Raymond|^Margaretta W. Rea|^Jane Rice|^Louise Rice|^Margaret Ronan|^Babette Rosmond|^Margaret St. Clair|^Lewis Padgett|^G. St. John-Loe|^I. M. Stephens|^Leslie F. Stone|^Doris Thomas|^Emma Vanne|^Ruth Washburn|^Helen Weinbaum|^Gabriel Wilson|^Lillian M. Ainsworth|^Thaedra Alden|^Pansy E. Black|^Dorothy Donnell Calhoun|^Clara E. Chesnutt|^Mollie Claire|^Clemence Dane|^Dorothy de Courcy|^Theodora Du Bois|^Norma Lazell Easton|^Augusta Groner|^Inez Haynes Irwin|^Millicent Holmberg|^Minna Irving|^Jessie Douglas Kerruish|^LesTina|^Winona McClintic|^Katherine Maclean|^Judith Merril|^Keith Hammond|^Hudson Hastings|^Maria Moravsky|^Marian O'Hearn|^Leslie Perri|^Margaretta W. Rea|^Amabel Redman|^Jane Rice|^Louise Rice|^Margaret Rogers|^M. F. Rupert|^Wilmar H. Shiras|^Francis Stevens|^Elma Wentz|^Gabriel Wilson|^Laura Withrow|^Frances Yerxa|^Vida Taylor Adams|^Marguerite Lynch Addis|^Edith M. Almedingen|^Frances Arthur|^Meredith Beyers|^Anne M. Bilbro|^Zealia B. Bishop|^Lady Anne Bonny|^Edna Goit Brintnall|^Mary S. Brown|^Dulcie Browne|^Loretta G. Burrough|^Brooke Byrne|^Grace M. Campbell|^Lenore E. Chaney|^Valma Clark|^Martha May Cockrill|^Ethel Helene Coen|^Eli Colter|^Mary Elizabeth Counselman|^Florence Crow|^Marjorie Darter|^Meredith Davis|^Miriam Allen de Ford|^Edith de Garis|^Leah Bodine Drake|^Elsie Ellis|^Mollie Frank Ellis|^Sophie Wenzel Ellis|^Betsy Emmons|^Mary McEnnery Erhard|^Caroline Evans|^Alice Drayton Farnham|^Effie W. Fifield|^Frances Garfield|^Louise Garwood|^Elizabeth Cleghorn Gaskell|^Myrtle Levy Gaylord|^Dorothea Gibbons|^Victoria Glad|^Gertrude Gordon|^Sonia H. Greene|^Allison V. Harding|^Lyllian Huntley Harris|^Margaret McBride Hoss|^Helen Rowe Henze|^Vennette Herron|^Terva Gaston Hubbard|^Mindret Lord|^Maebelle McCalment|^Laurie McClintock|^Sylvia Leone Mahler|^Isa-Belle Manzer|^Rachael Marshall|^Kadra Maysi|^Violet M. Methley|^Frances Bragg Middleton|^Bassett Morgan|^Sarah Newmeyer|^Dorothy Norwich|^Alice Olsen|^G. G. Pendarves|^Stella G. S. Perry|^Suzanne Pickett|^Mearle Prout|^Edith Lyle Ragsdale|^Ellen M. Ramsay|^Alicia Ramsey|^Sybla Ramus|^Helen M. Reid|^Susan Andrews Rice|^Eudora Ramsay Richardson|^Flavia Richardson|^Jean Richepin|^Katharine Metcalf Roof|^Gretchen Ruediger|^Edgar Saltus|^Sylvia B. Saltzberg|^Jane Scales|^Mary Sharon|^Schnirring|^Edna Bell Seward|^Ann Sloan|^Mrs. Chetwood Smith|^Lady Eleanor Smith|^Mrs. Harry Pugh Smith|^Emma-Lindsay Squier|^Marjorie Murch Stanley|^Francis Stevens|^Edith Lichty Stewart|^Pearl Norton Swet|^Gertrude Macaulay Sutton|^Tessida Swinges|^Fanny Kemble Johnson|^Mildred Johnson|^Helen W. Kasson|^Theda Kenyon|^Ida M. Kier|^Lois Lane|^Genevieve Larsson|^Greye La Spina|^Nadia Lavrova|^Helen Liello|^Signe Toksvig|^Louise Van de Verg|^Marilyn Venable|^Evangeline Walton|^Elizabeth Adt Wenzler|^Phyllis A. Whitney|^Everil Worrell|^Stella Wynne|^Katherine Yates|^Aalla Zaata|^L. M. Montgomery|^O. M. Cabral"))) %>%
  filter (str_detect (pub_year, ("^1926|^1927|^1928|^1929|^1930|^1931|^1932|^1933|^1934|^1935|^1936|^1937|^1938|^1939|^1940|^1941|^1941|^1942|^1943|^1944|^1945|^1946"))) %>%
  distinct () %>% group_by (author_canonical)  %>% filter (n() > 20) %>%
  select (pub_title, author_canonical)

#turn data into matrix, prepare for graphing

(set.seed(42))

pulp_women_matrix <- as.matrix (pulp_women_df) 
pulp_women_graph <- graph.edgelist (pulp_women_matrix, directed=F)

#add colors to nodes

vcolors <- rep("orange", vcount(pulp_women_graph))
vcolors [V(pulp_women_graph)$name == "Amazing"] <- "cyan"
vcolors [V(pulp_women_graph)$name == "Weird"] <- "mediumvioletred"
vcolors [V(pulp_women_graph)$name == "Astounding"] <- "royalblue4"
vcolors [V(pulp_women_graph)$name == "Wonder"] <- "plum"
vcolors [V(pulp_women_graph)$name == "Fantastic"] <- "gray0"
vcolors [V(pulp_women_graph)$name == "Startling"] <- "red4"
vcolors [V(pulp_women_graph)$name == "Planet"] <- "springgreen4"

plot (pulp_women_graph, vertex.color=vcolors, vertex.label.cex=.5, vertex.size=5)


```
